---
title: "The S3 class system"
author: "Aaron Baker"
topic: "05"
layout: post
root: ../../../
---
Below is an example of how to create a new S3 class. Now when I think of something new and shiny, I think of muscle cars. Don't ask me why as muscle cars are actually really old, but logic isn't the key here. Suppose that we wanted a new class, for some reason, to store within it the top 3 muscle car preferences of a car enthusiast, and their rankings on a scale of 1-10 of adoration, as well as say, the horsepower of their engine and mpg rating. The first step is to create a list that contains the information that we wish to store, like so
```{r}
#Create an object

VROOM <- list(cars = c("car1", "car2", "car3"), Rating = c(10,10,10), HP = c(-999,-999,-999), MPG = c(-999,-999,-999))
class(VROOM)

#Assign the object VROOM to class classiccar
class(VROOM) <- append(class(VROOM),"classiccar")
class(VROOM)
```
Now the idea is that for this class, we might have special functions that apply uniquey to how it works that might work differently on a different S3 object (like mean). So, perhaps we want to know, by some far out gnarly reason, the mean and standard deviation of the rating and horsepower for a classiccar object(s). So, we create a function that will give us that information from a classiccar object.To not mess with the underlying "mean" function and to build from scratch I will use mean2.

```{r}
mean2 <- function(x)
 {
     UseMethod("mean2")
 }

 mean2.classiccar <- function(x)
 {
    return(c(mean(x$Rating), mean(x$HP)))
 }

 mean2(VROOM)

```

Here of course we would prefer perhaps the real outcome from say, some muscle car maniac:

```{r}
VROOM <- list(cars = c("1970 GTO 500", "1978 Superbee", "1968 Plymouth Road Runner"), Rating = c(10,9.8,9), HP = c(543,480,530), MPG = c(10.5,9.8,9))
class(VROOM)
class(VROOM) <- append(class(VROOM),"classiccar")

mean2(VROOM)
```

And so the results will follow.
